---
title: "Samba_GA_SA"
author: "Choe Samba"
date: "November 4, 2018"
output:
  word_document: default
  html_document: default
---

```{r}
library('ggplot2')
library('quantmod')
library('GA')
library('GenSA')
```


```{r}
library("quantmod")
tickers <- c("GOOG", "TRQ", "AMZN", "PGR", "TWTR")
getSymbols(tickers, from = "2017-01-01", to = "2018-10-30")
P <- NULL
for(ticker in tickers) {
 tmp <- Cl(to.monthly(eval(parse(text = ticker))))
 P <- cbind(P, tmp)
}
colnames(P) <- tickers
R <- diff(log(P))
R <- R[-1,]
mu <- colMeans(R)
sigma <- cov(R)
library("PerformanceAnalytics")
pContribCVaR <- ES(weights = rep(0.2, 5), method = "gaussian", portfolio_method = "component", mu = mu, sigma = sigma)$pct_contrib_ES
obj <- function(w) {
 fn.call <<- fn.call + 1
 if (sum(w) == 0) { w <- w + 1e-2 }
 w <- w / sum(w)
 CVaR <- ES(weights = w, method = "gaussian", portfolio_method = "component", mu = mu, sigma = sigma)
 tmp1 <- CVaR$ES
 tmp2 <- max(CVaR$pct_contrib_ES - 0.225, 0)
 out <- tmp1 + 1e3 * tmp2
 return(out)
}
```

```{r}

objective <- function(w) {
 fn.call <<- fn.call + 1
 if (sum(w) == 0) { w <- w + 1e-2 }
 w <- w / sum(w)
 CVaR <- ES(weights = w, method = "gaussian", portfolio_method = "component", mu = mu, sigma = sigma)
 tmp1 <- CVaR$ES
 tmp2 <- min(CVaR$pct_contrib_ES - 0.225, 0)
 out <- tmp1 + 1e3 * tmp2
 return(out)
 
}


```

## GA
```{r}
set.seed(1234)
fn.call <<- 0
gap <- ga(type = "real-valued",fitness=obj,lower=rep(0,5),upper=rep(1,5), popSize = 50,maxiter = 150, pcrossover = 0.75, pmutation = 0.1)

summary(gap)


```



## GENSA
```{r}
set.seed(9999)
fn.call <<- 0


out.GenSA <- GenSA(fn = obj, lower = rep(0, 5), upper = rep(1, 5), control = list(smooth = FALSE, max.call = 3000))
fn.call.GenSA <- fn.call
out.GenSA$value
out.GenSA$counts
cat("GenSA call functions", fn.call.GenSA, "times.\n")
wstar.GenSA <- out.GenSA$par
wstar.GenSA <- wstar.GenSA / sum(wstar.GenSA)
rbind(tickers, round(100 * wstar.GenSA, 2))
100 * (sum(wstar.GenSA * mu) - mean(mu))
wstar.GenSA
```

```{r}
gen_solution<-c(0.20427575, 0.05866408, 0.09714570, 0.51204626, 0.12786821)
gap_solution<-c(0.1739779, 0.03611608, 0.014552, 0.7534922, 0.8972672)
result <-cbind(gap_solution,gen_solution)
row.names(result)<-c("GOOG","TRQ","AMZN","PGR","TWTR")
result
```

```{r}



```


Q.2 In this problem, you will apply both GA and SA to search for the optimal parameters in a regression. Do the following:
Create a dataset with with 20 X, Y values. You may use the same dataset that you used in Dr. Razavi's class.
Use GA and SA to search for optimal b0 and b1 estimates. The objective should be to minimize  SSE (sums of square error). How does this compare to the exhaustive search you did in your class?
Plot your solution, and the optimal regression line (using the built-in function). Clearly label the output.
  
# Finding b0 and b1 value manually
```{r}
x=c(58,60,61,67,69,72,76,79,82,89,95,97)
y=c(2.98,3.08,3.42,3.89,4.01,4.22,4.56,4.8,5.02,5.45,6.54,7.56)
## ss= sum square 
ssxy=sum((x-mean(x))*(y-mean(y)))
ssx=sum((x-mean(x))^2)

```

```{r}
b1= ssxy/ssx
b1

```

```{r}
b0=mean(y)-b1*mean(x)
b0

```

```
  }
```


```{r}
object_ga_sa <- function(x=c(58,60,61,67,69,72,76,79,82,89,95,97),y=c(2.98,3.08,3.42,3.89,4.01,4.22,4.56,4.8,5.02,5.45,6.54,7.56)){sum((y-(b0-b1*x))^2)}
```

```{r}
ga_REG <- ga(type = "real-valued", fitness=obj, lower = rep(0, 5), upper = rep(1, 5),popSize = 50,maxiter = 150)
summary(ga_REG)

```

```{r}
lm(b0~b1)

```
```{r}
plot(ga_REG)
```

```{r}
gen_REG <- GenSA(fn = object_ga_sa, lower = rep(0,2), upper = rep(0.03, 2), control = list(smooth = FALSE, max.call = 3000))
gen_REG
```

```{r}
n =object_ga_sa
ll = c(0)
ul = c(2)
par = 2
out1 <- GenSA(par=par,lower=ll,upper=ul,fn=n)
out1[c("value","par","counts")]
curve(nfun, from = 0, to = 2, n = 10)
points(out1$par[1],-out1$value, col = 2, pch = 1)
```

